\documentclass[a4paper,10pt]{article}
%\documentclass[a4paper,10pt]{scrartcl}

\usepackage[utf8]{inputenc}

\title{Sprint 1 Team 9 Hashgraph Backlog}
\author{Wernich Baumgarten \textless 19896913 \textgreater \\
	Simon Dennis \textless 19770235 \textgreater  \\
	Oliver Gilbey \testless 17839688 \textgreater  \\
	Ryan Lang \textless 19066171 \textgreater  \\
	Simon\'e van Zyl \textless 18395317 \textgreater  \\
	Bernard Wiesner \textless 19790155 \textgreater}
\date{}

\begin{document}
\maketitle
\section{Sprint 1 Backlog}
\subsection{US1: As a user, I want a web based interface, so that I can view it in a browser.}
Completed
\begin{itemize}
 \item Flask webserver
 \item HTML page
 \item Python integration of HTML and Flask
 \item Must display in Firefox and Chrome
\end{itemize}
Incomplete
\begin{itemize}
 \item Server must be stable
\end{itemize}

\subsection{US2: As a user, I want the graph to dynamically update, so that I don’t have to constantly refresh the page.}
Completed
\begin{itemize}
 \item The graph must only update when a new transaction occurs
 \item Graph requires X, Y co-ordinates
\end{itemize}
Incomplete
\begin{itemize}
 \item Only the graph must update on the HTML page
\end{itemize}

\subsection{US3: As a user, I want to be able to change the number of nodes visualised, so that the width of gossip can be visualised at varying scale.}
Completed
\begin{itemize}
 \item Slider bar on the web interface to change the number of nodes
\end{itemize}
Incomplete
\begin{itemize}
 \item Implement functionality into data extraction.
 \item Test to find max number of nodes for processing.
 \item Limit slider to the max number of nodes.
\end{itemize}

\subsection{US4: As a user, I want a start and stop button, so that I can capture the graph over a specific period of transactions.}
Completed\\
None\\
Incomplete
\begin{itemize}
 \item On click of start button, restart the live data extraction.
 \item On click of start button, the visual must be restarted.
 \item On click of stop button, the visual must stop.
\end{itemize}

\subsection{US5: As a user, I want a save button to export the graph findings, so that I can save the resulting session for comparison later.}
Completed\\
None\\
Incomplete
\begin{itemize}
 \item On save button click, export the visual to an image file.
\end{itemize}

\subsection{US6: As a user, I want a visual representation of the HashGraph, so that I can verify finality.}
Completed
\begin{itemize}
 \item The graph data must be available
 \item Graph must be plotted.
 \item Graph must be displayed in web interface.
\end{itemize}
Incomplete
\begin{itemize}
 \item Graph theory must be applied.
\end{itemize}

\end{document}
